### 2024-10-19 research-methods.qmd
20241019 - hypothesis and prediction

@@

For instance, we may be interested to evaluate whether players perform better (e.g., run faster) if they drink a sports drink compared when they drink only water.
Our hypothesis might be that players will be expected to perform better when they drink a sports drink (compared to when they drink only water).
To this this research question and hypothesis, we might conduct an experiment by randomly assigning some players during practice to receive a sports drink and some players to receive only water.
In this case, our independent variable is whether the player receives a sports drink.
Our dependent variable might be their 40-yard dash time during practice.

>>>>

## Research Questions, Hypotheses, and Predictions {#sec-hypothesisVsPrediction}

A research question is a question that the investigator (you!) want to know the answer to.
For example, a research question might be: "Does consumption of sports drink improve player performance?"
A hypothesis is a proposed explanation.
A prediction is "the expected result of a test that is derived, by deduction, from a hypothesis or theory" [@Eastwell2014, p. 17; archived at <https://perma.cc/8EX4-8JYN>].
Here is an example of a hypothesis and the resulting prediction:

> The present study evaluates whether consumption of sports drink improves player performance.
> I <u>*hypothesize*</u> that consumption of sports drink leads football players to perform better in games because of greater endurance owing to restoration of electrolytes.
> If the hypothesis is true, I <u>*predict*</u> that players who consume sports drink during a game will score more fantasy points than players who do not consume sports drink during the game.

@@

For instance, we may be interested to evaluate whether players perform better (e.g., run faster) if they drink a sports drink compared when they drink only water.
Our hypothesis might be that players will be expected to perform better when they drink a sports drink (compared to when they drink only water), for the reasons specified in @sec-hypothesisVsPrediction.
To this this research question and hypothesis, we might conduct an experiment by randomly assigning some players during practice to receive a sports drink and some players to receive only water.
In this case, our independent variable is whether the player receives a sports drink.
Our dependent variable might be their 40-yard dash time during practice.
